Pythran: Bringing OpenMP to a Python Subset

### 2013-02-03 doc/papers/europar2013/paper.tex
A few reformatting later.

    \begin{lstlisting}[label={lst:cython-sample}, caption={Cython Impelmentation
    of a Parallel Reduction.}]
import math
cimport cython
from cython.parallel import parallel, prange
from libc.math cimport sqrt
def sum_sqrt():
    cdef float r = 0
    cdef int i
    with nogil, parallel():
        for i in prange(10000000):
            r += sqrt(i)
    return r
\end{lstlisting}
\end{figure}
%
\begin{figure}[ht]
    \begin{lstlisting}[label={lst:pythran-sample}, caption={Cython Impelmentation
    of a Parallel Reduction.}]
#pythran export sum_sqrt()
import math
def sum_sqrt():
    r = 0
    "omp parallel for private(i) reduction(+:r)"
    for i in xrange(10000000):
        r += math.sqrt(i)
    return r
    \end{lstlisting}
\end{figure}

>>>>

    \begin{lstlisting}[label={lst:cython-sample}, caption={Cython implementation
    of a parallel reduction.}]
import math
cimport cython
from cython.parallel import parallel, prange
from libc.math cimport sqrt
def sum_sqrt():
    cdef float r = 0
    cdef int i
    with nogil, parallel():
        for i in prange(10000000):
            r += sqrt(i)
    return r
\end{lstlisting}
\end{figure}
%
\begin{figure}[ht]
    \begin{lstlisting}[label={lst:pythran-sample}, caption={Cython implementation
    of a parallel reduction.}]
#pythran export sum_sqrt()
import math
def sum_sqrt():
    r = 0
    "omp parallel for private(i) reduction(+:r)"
    for i in xrange(10000000):
        r += math.sqrt(i)
    return r
    \end{lstlisting}
\end{figure}
